\subsection{A. K. Nandakumaran}

The main theme of the research is to understand the asymptotic analysis of  PDE problems and related optimal control problems in some complex domains. We consider domains whose boundary is rapidly oscillating which  leads to multi-scales in the problem. One of the major issue is the development of the so called unfolding operators which contains information about both scales. We have ingeniously used the unfolding operators not only to carry out the limiting behaviour of the problem under study, it is used to characterize the optimal controls. One needs to construct suitable such operators according to the type of domain and the problem [1], [3-5]. On a completely different direction, a multi-step Volterra integral equation-based algorithm was developed to measure the electric field auto-correlation function from multi-exposure speckle contrast data. This enabled us to derive an estimate of the full diffuse correlation spectroscopy data-type from a low-cost, camera-based system. This method is equally applicable for both single and multiple scattering field auto-correlation models. The feasibility of the system and method was verified using simulation studies, tissue mimicking phantoms and subsequently in in vivo experiments [2].


\subsection{Abhishek Banerjee}




\subsection{Apoorva Khare}

(1) I extended a fundamental matrix inequality, the Schur Product Theorem, for positive definite matrices, by providing nonzero, tight lower bounds. (2) I improved and updated several preprints - notably, a comprehensive work titled "Moment-sequence transforms" with Belton-Guillot-Putinar.


\subsection{Arvind Ayyer}

In joint work with Aas, Linusson and Potka [1], the exact phase diagram for a semipermeable TASEP with nonlocal boundary jumps was obtained. In joint work with Behrend [2], new factorization theorems for classical group characters were proved. Applications to alternating sign matrices and plane partitions were given. In joint work with Finn and Roy [3], the phase diagram for a multispecies left-permeable asymmetric exclusion process was derived. In joint work with Linusson [4], a new class of reverse juggling processes was defined and their stationary distributions were computed.


\subsection{Basudeb Datta}

A semi-regular tiling of the hyperbolic plane is a tessellation by regular geodesic polygons with the property that each vertex has the same vertex-type. Determined combinatorial criteria for the existence, and uniqueness, of a semi-regular tiling with a given vertex-type \ref{bdsg_2019} .


\subsection{Dilip P. Patil}

COMPUTATIONAL ASPECTS OF BURNSIDE RINGS PART II: IMPORTANT MAPS (Jointly Martin  Kreuzer)   The Burnside ring B(G) of a finite group G, a classical tool in the representation theory of finite groups, is studied from the point of view of computational algebra. In the rst part (cf. [8]) we examined the ring theoretic properties of B(G) using the methods of computer algebra. In this part we shift our focus to important maps between two Burnside rings and make several well-known maps of representation theory explicitly computable. The inputs of all our algorithms are the tables of marks of the two groups, and the outputs are matrices of integers representing the maps via their image in the ghost ring. All algorithms have been implemented in the computer algebra system ApCoCoA and are illustrated by applying them to explicit examples. Especially, we study the restriction and induction maps, the projection and in ation maps, the conjugation isomorphism, and the Frobenius-Wielandt homomorphism.


\subsection{E K Narayanan}

Positivity properties and asymptotics of Heckman-Opdam hypergeometric functions associated to root system to type BC with non-positive multiplicity functions were studied in detail.


\subsection{Gadadhar Misra}

There is a one to one correspondence between holomorphic imprimitivities and the holomomorphic hermitian homogeneous vector bundles on a bounded symmetric domain D. The homogeneous bundles can be obtained by holomorphic induction from representations of a certain parabolic Lie algebra on finite dimensional inner product spaces. The representations, and the induced bundles, have composition series with irreducible factors. In joint work with A. Koranyi, our first main result is the construction of an explicit differential operator intertwining the bundle with the direct sum of its factors. Next, we study Hilbert spaces of sections of these bundles. We use this to get, in particular, a full description and a similarity theorem for homogeneous n-tuples of operators in the Cowen-Douglas class of the Euclidean unit ball.   Beurling’s theorem shows that all submodules of the Hardy module are isomorphic leading to the question of rigidity of submodules in multi-variate operator theory. The submodules of analytic Hilbert modules defined over certain algebraic varieties in bounded symmetric domains, the so-called Jordan-Kepler varieties X of arbitrary rank r have been studied. For r > 1, the singular set of X is not a complete intersection. Hence the usual monoidal transformations do not suffice for the resolution of the singularities. Instead (joint with Upmeier), we describe a new higher rank version of the blow-up process, defined in terms of Jordan algebraic determinants, and apply this resolution to obtain the rigidity of the sub-modules vanishing on the singular set.   (with Koranyi) Homogeneous Hermitian holomorphic vector bundles and the Cowen-Douglas class over bounded symmetric domains, Adv. Math., 351 (2019), 1105 - 1138.  (with Upmeier)  Singular Hilbert modules on Jordan-Kepler varieties, To appear, Proceedings of IWOTA 2018, in memory of R. G. Douglas.


\subsection{Gautam Bharali}

A detailed investigation of the Bergman geometry of domains whose boundaries have isolated infinite-type points was completed. Optimal estimates, from above and below, for the growth of the Bergman kernel (on the diagonal) and the Bergman metric, as one approaches an infinite-type boundary point, were obtained. The class of domains that were studied subsumes all classes of domains that have previously been considered in the literature. These results have appeared in the paper [1].  [1] Bharali, Gautam, On the growth of the Bergman metric near a point of infinite type, J. Geom. Anal. , 30 (2020), 1238-1258.


\subsection{Govindan Rangarajan}

We constructed [1] symmetry preserving and symmetry broken N-bright, dark and antidark soliton solutions of a nonlocal nonlinear Schrödinger equation. To obtain these solutions, we used appropriate eigenfunctions in Darboux transformation (DT) method. Further, we derived two dark/antidark soliton solution with the help of DT method. In the dark/antidark soliton solution case we observed a contrasting behaviour between the envelope of the ﬁeld and parity transformed complex conjugate envelope of the ﬁeld. For a particular parametric choice, we got dark (antidark) soliton for the ﬁeld while the parity transformed complex conjugate ﬁeld exhibits antidark (dark) soliton. Due to this surprising result, both the ﬁeld and PT transformed complex conjugate ﬁeld exhibit sixteen different combinations of collision scenario.   We presented observational evidence [2] from studies on primary cortical cultures from AD transgenic mice for significant decrease in total spine density at DIV-15 and onward. This indicates reduction in potential healthy synapses and strength of connections among neurons. Based on this, a network model of neurons was developed, that explains the consequent loss of coordinated activity and transmission efficiency among neurons that manifests over time. The critical time when structural connectivity in the brain undergoes a phase-transition, from initial robustness to irreparable breakdown, is estimated from this model. We also showed how the global efficiency of signal transmission in the network decreases over time. Moreover, the number of multiple paths of high efficiency decreased rapidly as the disease progresses, indicating loss of structural plasticity and inefficiency in choosing alternate paths or desired paths for any pattern of activity. Thus loss of spines caused by β-Amyloid (Aβ) peptide results in disintegration of the neuronal network over time with consequent cognitive dysfunctions in Alzheimer’s Disease (AD).  We investigated [3] the effect of four-wave mixing in the interactions among nonlinear waves such as solitons, breathers, and rogue waves of a coupled generalized nonlinear Schrodinger equation. We explored several interesting results including superposition of breather pulses, increment in the number of breather pulses and in amplitudes of breathers, and rogue waves. By strengthening the four-wave mixing parameter, we observed different transformations that occur between different localized structures. For instance, we visualized a transformation from bright soliton to breather form, bright and dark rogue wave to four-petaled rogue wave structures, four-petaled rogue wave to other rogue wave forms, and so on. Another important observation was that the interaction of a bright soliton with a rogue wave in the presence of the four-wave mixing effect provides interaction between a dark oscillatory soliton and a rogue wave.  [1] Vishnu Priya, N., Senthilvelan, M.,  Rangarajan, G. & Lakshmanan, M. On symmetry preserving and symmetry broken bright, dark and antidark soliton solutions of nonlocal nonlinear Schrödinger equation, Physics Letters A, 383, 15 (2019).   [2] Kashyap, G. A. R. S. R. K., Bapat, D., Das, D., Gowaikar, R. D., Amritkar, R. E., Rangarajan, G., Ravindranath, V. & Ambika, G., Synapse loss and progress of Alzheimer’s disease - A network model, Scientific Reports, 9, 6555 (2019).   [3] Vishnu Priya, N., Senthilvelan, M. &  Rangarajan, G, On the role of four-wave mixing effect in the interactions between nonlinear modes of coupled generalized nonlinear Schrodinger equation, Chaos, 29, 123135 (2019).


\subsection{Hrish Seshadri}




\subsection{Kaushal Verma}

For a given pair of smoothly bounded planar domains $D_1, D_2$, it was shown in \cite{1} that the product of the Carath\'{e}odory metrics on them is bounded from below by the product of the Carath\'{e}odory metrics on their union and intersection up to a multiplicative factor. This shows that the S\"{z}ego kernels on $D_1, D_2, D_1 \cap D_2$ and $D_1 \cup D_2$ are related by the same inequality.    The Suita conjecture in higher dimensions is a paradigm that asks for the limiting boundary values of the product of the Bergman kernel (on the diagonal) and the volume of the Kobayashi indicatrix. This object is a biholomorphic invariant and is known to admit universal bounds on convex domains. Its limiting behaviour was clarified on strongly peudoconvex domains and egg domains in $\mathbb C^2$. See \cite{2}.  The boundary behaviour of several classical conformal invariants were studied in \cite{3}.  The relationship between the Fridman invariant and the Squeezing function was clarified in \cite{4}.  The relation between a pair of H\'{e}non maps that share the same forward and backward Julia sets was clarified in \cite{5}.


\subsection{Mahesh Kakde}

Jointly with Samit Dasgupta from Duke University I resolved the Brumer-Stark conjecture during the said period. We spoke about it at the "International Colloquium" in January 2020 in TIFR. Further, a paper on higher Chern classes written a while ago (jointly with Frauke Bleher, Ted Chinburg,  Ralph Greenberg, George Pappas, Romyar Sharifi and Martin Taylor) was accepted for publication in American Journal of Mathematics.


\subsection{Manjunath Krishnapur}

Completed a study of law of iterated logarithm for last passage percolating on the two dimensional integer lattice [1]. Other studies on absolute continuity of limiting spectral distributions, a proof of KMT theorems, study of discrete nodal length, a problem on amplitude constrained Gaussian channel and some problems on nodal domains of random functions are in various stages of completion.  [1] Lower Deviations in β-ensembles and Law of Iterated Logarithm in Last Passage Percolation.   Authors: Riddhipratim Basu, Shirshendu Ganguly, Milind Hegde, Manjunath Krishnapur. arXiv:1909.01333


\subsection{Mrinal Kanti Ghosh}

Risk-sensitive stochastic differential games have been studied in the nonnegative orthant [1] and the whole space [2]. Existence of saddle point/Nash equilibria for relevant cases have been derived.


\subsection{Purvi Gupta}

Note: this description is for research carried out during the period February 11, 2020 (date of joining) to March 31, 2020.   In this period,  I completed and submitted a manuscript ([1]),  based on joint work with C. U. Wawrzyniak. This work studies the stability of the solution of the so-called global Bishop problem (a plateau-type problem) for a model real $n$-dimensional sphere in $\mathbb{C}^n$, $n\geq 2$. In this problem, the solution is required, among other things, to be foliated by holomorphic disks (i.e., Levi-flat) attached to the given sphere. This structure is significant in complex analysis for multiple reasons. The general Bishop problem, although very well-understood in two (complex) dimensions, is wide open in dimensions three and higher, and our work is the first global result in this direction.    References [1] Gupta, Purvi and Wawrzyniak, Chloe Urbanski, Stability of the hull(s) of an $n$-sphere in $\mathbb{C}^n$. Submitted.


\subsection{R VENKATESH}

(a) Settled the decomposition theorem for G-stable affine Demazure modules for the cases $G = E_6,7,8$ and $F_4$ and thus completed the main theorems of the papers of V. Chari and et al., (J. Algebra, 2016) and Deniz Kus and et al., (Represent. Theory., 2016). Obtained a new combinatorial proof for the key fact that was used in  V. Chari and et al., (J. Algebra, 2016) to prove the decomposition of G-stable affine Demazure modules. This key fact was proved only for the cases when G is the classical type and $G_2$ in their paper and they also proved it by analysing case-by-case. Our proof is uniform avoids the case-by-case analysis and works for all finite-dimensional simple Lie algebras.  (b) Simplified the presentation of all affine Demazure modules of untwisted affine Kac–Moody Lie algebras. Simplifying the generators and relations of these modules is very crucial in their study. We are investigating how to use this simplified presentation of affine Demazure modules to study Schur positivity type questions which arise naturally in Algebraic Combinatorics.   (c) A number of conjectures made about the graded characters affine Demazure modules of affine $sl_3$ using data obtained from SAGE. 


\subsection{R. Venkatesh}

(a) Settled the decomposition theorem for G-stable affine Demazure modules for the cases $G = E_6,7,8$ and $F_4$ and thus completed the main theorem of the paper of V. Chari and et al., (J. Algebra, 2016). Obtained a new combinatorial proof for the key fact that was used in  V. Chari and et al., (J. Algebra, 2016) to prove the decomposition of G-stable affine Demazure modules. This key fact was proved by V. Chari and et al., (J. Algebra, 2016) only for the cases when G is the classical types and $G_2$ and they did a case-by-case analysis to prove this. Our new proof is very uniform and avoids the case-by-case analysis and works in general.  (b) Simplified the presentation of all affine Demazure modules of untwisted affine Kac–Moody Lie algebras. Simplifying the generators and relations of these modules is very crucial in their study. We are investigating how to use this simplified presentation of affine Demazure modules to study Schur positivity type questions which arise naturally in Algebraic Combinatorics.   (c) A number of conjectures made about the graded characters affine Demazure modules of affine $sl_3$ using data obtained from SAGE. 


\subsection{RADHIKA GANAPATHY}

1) Let $G$ be a split connected reductive group over $\mathbb{Z}$. Let $F$ be a non-archimedean local field. With $K_m := Ker(G(O_F ) → G(O_F /p_{m,F} ))$, Kazhdan proved that for a field $F′$ sufficiently close to $F$, the Hecke algebras $\mathcal{H}(G(F), K_m)$ and $\mathcal{H}(G(F′), K_m′ )$ are isomorphic, where $K_m′$ denotes the corresponding object over $F′$. I have generalized this result to general connected reductive groups [1].  2) In my earlier work, I had established  a variant of the Kazhdan isomorphism for split reductive groups (by replacing $K_m$ replaced by the $m$-th filtration subgroup of the Iwahori subgroup). I have been working on generalising this result to general connected reductive groups. As part of this work, I have chosen a nice set of representatives in $G(F)$ for the elements of the extended affine Weyl group. This set of representatives has some very interesting properties (for instance, it is compatible with unramified descent), and is useful in the study of representation theory of $p$-adic groups.   [1] A Hecke algebra isomorphism over close local fields, preprint, 12 pages.


\subsection{SANCHAYAN SEN}

In [1], we provide an explicit algorithm for sampling a uniform simple connected random graph with a given degree sequence. By products of this central result includes scaling limits for the metric space structure of the maximal components in the critical regime of both the configuration model and the uniform simple random graph model with prescribed degree sequence under finite third moment assumption on the degree sequence. As a substantive application we answer a question raised by Černý and Teixeira, Random Structures Algorithms (2013), by obtaining the metric space scaling limit of maximal components in the vacant set left by random walks on random regular graphs.  In [2], we study limits of the largest connected components (viewed as metric spaces) obtained by critical percolation on uniformly chosen graphs and configuration models with heavy-tailed degrees. We develop general principles under which the scaling limits can be obtained. Of independent interest, we derive refined asymptotics for various susceptibility functions and the maximal diameter in the barely subcritical regime.  In [3], we give alternate constructions of (i) the scaling limit of the uniform connected graphs with given fixed surplus, and (ii) the continuum random unicellular map of a given genus that start with a suitably tilted Brownian continuum random tree and make `horizontal' point identifications, at random heights, using the local time measures. In particular, this yields a breadth-first construction of the scaling limit of the critical Erdős-Rényi random graph which answers a question posed by Addario-Berry, Broutin, and Goldschmidt, Probab. Theory Related Fields (2012). As a consequence of this breadth-first construction we obtain descriptions of the radii, the distance profiles, and the two point functions of these spaces in terms of functionals of tilted Brownian excursions.    [1] Geometry of the vacant set left by random walk on random graphs, Wright's constants, and critical random graphs with prescribed degrees Authors: Shankar Bhamidi, Sanchayan Sen Journal: Random Structures & Algorithms (First published on 25 July 2019)  [2] Universality for critical heavy-tailed network models: Metric structure of maximal components Authors: Shankar Bhamidi, Souvik Dhara, Remco van der Hofstad, Sanchayan Sen Journal: Electronic Journal of Probability (Accepted in December 2019)  [3] On breadth-first constructions of scaling limits of random graphs and random unicellular maps Authors: Grégory Miermont, Sanchayan Sen ArXiv preprint https://arxiv.org/abs/1908.04403 (Announced in August 2019)


\subsection{Siddhartha Gadgil}

We continued our development of automated theorem proving systems. Specifically, we developed a framework based on equation terms to allow accumulation of knowledge and facilitate deep learning and hybrid autonomous/interactive execution.


\subsection{Soumya Das}

Work on the determination of Siegel modular forms by their fundamental Fourier coefficients was done including a mod p version. Study of Fourier coefficients and sup-norms of modular forms was continued.


\subsection{Srikanth Krishnan Iyer}

We study combinatorial connectivity for two models of random geometric complexes. These two models - \v{C}ech and Vietoris-Rips complexes - are built on a homogeneous Poisson point process of intensity $n$ on a $d$-dimensional torus, $d > 1$, using balls of radius $r_n$. Given a (simplicial) complex (i.e., a collection of $k$-simplices for all $k \geq 1$), we can connect $k$-simplices via $(k+1)$-simplices (`up-connectivity') or via $(k-1)$-simplices (`down-connectivity). Our interest is to understand these two combinatorial notions of connectivity for the random \v{C}ech and Vietoris-Rips complexes asymptotically as $n \to \infty$. Our results give tighter bounds on the constants in the logarithmic scale as well as shed light on the possible second-order correction factors. Further, they also reveal interesting differences between the phase transition in the \v{C}ech and Vietoris-Rips cases. The analysis is interesting due to non-monotonicity of the number of isolated $k$-faces (as a function of the radius) and leads one to consider `monotonic' vanishing of isolated $k$-faces. The latter coincides with the vanishing threshold mentioned above at a coarse scale (i.e., $\log n$ scale) but differs in the $\log \log n$ scale for the \v{C}ech complex with $k = 1$ in the up-connected case. For the case of up-connectivity in the Vietoris-Rips complex and for $r_n$ in the critical window, we also show a Poisson convergence for the number of isolated $k$-faces when $k \leq d$. [1]


\subsection{Subhojoy Gupta}

(1) With Mahan Mj (TIFR)  we completed a  research program concerning meromorphic projective structures on surfaces and their monodromy representations. We used new  work of Allegretti-Bridgeland, together with older ideas of Thurston, to develop a geometric understanding of these structures on punctured surfaces, and prove analogues of results of Hejhal and Gallo-Kapovich-Marden -- see [1] and [2]. In an independent paper [3], I used our the techniques we had developed, to shed light on a remark of Poincaré in 1883. This complemented other projects concerning meromorphic quadratic differentials (see [8] and [10]).  (2) In joint work [4] with Indranil Biswas (TIFR), Mahan Mj (TIFR) and Junho Whang (MIT), we classified the finite mapping class group orbits in the PSL(2,C) character variety.  (3) In a project with Basudeb Datta (IISc) we revised and published a paper [5] developing an algorithmic technique of constructing semi-regular tilings of the hyperbolic plane. We expect this to have an impact on tilings-related research, which is an active area that has an intersection with several fields like combinatorics, computational geometry and group theory.   (4)  With Harish Seshadri (IISc) we wrote a paper [6], and a survey [7], concerning the complex geometry of Teichmüller spaces, where we investigated the convexity (or lack thereof) of the boundary of complex domains biholomorphic to Teichmüller space. We have ongoing conversations regarding other questions that lie at the intersection of several complex variables, differential geometry and Teichmüller theory.   (5) A paper with Indranil Biswas (TIFR) and Sorin Dumitrescu (UCA)  concerning branched projective structures on surfaces was published [9]. In an ongoing project, we aim to understand the symplectic geometry of the space of such structures better.  [1] Meromorphic projective structures, grafting and the monodromy map, submitted, available at http://arxiv.org/abs/1904.03804. [2] Monodromy representations of meromorphic projective structures, Proc. Amer. Math. Soc. 148 (2020), no. 5, 2069–2078. [3] Monodromy groups of CP1-structures on punctured surfaces, submitted, available at https: //arxiv.org/abs/1909.10771. [4] Surface group representations in SL(2,C) with finite mapping class orbits, submitted, available at https://arxiv.org/ abs/1707.00071. [5] Semi-regular tilings of the hyperbolic plane, to appear, Discrete and Computational Geometry (2019), available at https://doi.org/10.1007/s00454-019-00156-0. [6] On domains biholomorphic to Teichmüller spaces, International Mathematics Research Notices, Volume 2020, Issue 8, (2020), 2542–2560. [7] Complex geometry of Teichmüller domains, Handbook of Teichmüller theory Vol VII, 63–88, IRMA Lect. Math. Theor. Phys., 30, Eur. Math. Soc., Zürich, 2020. [8] Holomorphic quadratic differentials in Teichmüller theory, Handbook of Teichmü ller theory Vol VII, 2020. [9] Branched projective structures on a Riemann surface and logarithmic connections, Documenta Mathematica 24 (2019), 2299–2337. [10] Limits of harmonic maps and crowned hyperbolic surfaces, Trans. Amer. Math. Soc. 372 (2019), no. 11, 7573–7596.


\subsection{Sundaram Thangavelu}

In a joint work with Pritam Ganguly  we have investigated the $ L^p $  boundedness of the lacunary maximal function $ M_{\mathbb{H}^n}^l $ associated to the spherical means $ A_r f$  taken over Koranyi spheres on the Heisenberg group. Closely following an approach used by M. Lacey in the Euclidean case, we obtain sparse bounds for these maximal functions leading to new unweighted and weighted estimates. The key ingredients in the proof are the $L^p$  improving property of the operator $ A_r $  and a continuity property of the difference $ A_r f−\tau_y A_r f,$ where $\tau_yf(x)=f(xy−1) $ is the right translation operator.


\subsection{Thirupathi Gudi}

We have developed a Hybrid High Order methods for elliptic obstacle problem in both two and three space dimensions allowing general meshes. The gap in literature of developing an optimal order convergent method using quadratic finite element method is resolved under the realistic regularity. In another work, we derived optimal order finite element analysis for constrained Dirichlet boundary optimal control problem. We have also studied numerous finite element methods for parabolic obstacle problem under the realistic regularity.


\subsection{Tirthankar Bhattacharyya}

1. Distinguished varieties:  A distinguished algebraic variety in $\mathbb{C}^2$ has been the focus of much research in recent years because of good reasons. We have given a different perspective.  \begin{enumerate}  \item We have found a new characterization of an algebraic variety $\mathcal W$ which is distinguished with respect to the bidisc. It is in terms of the joint spectrum of a pair of commuting linear matrix pencils.  \item There is a characterization known of $\mathbb{D}^2\cap\mathcal{W}$ due to a seminal work of Agler and McCarthy. We have shown that Agler--McCarthy characterization can be obtained from the new one and vice versa.  \item En route, we develop a new realization formula for operator-valued contractive analytic functions on the unit disc.  \item There is a one-to-one correspondence between operator-valued contractive holomorphic functions and {\em canonical model triples}. This pertains to the new realization formula mentioned above.  \item Pal and Shalit gave a characterization of an algebraic variety, which is distinguished with respect to the symmetrized bidisc, in terms of a matrix of numerical radius no larger than $1$. We refine their result by making the class of matrices strictly smaller.  \item In a generalization in the direction of more than two variables, we have characterized all one-dimensional algebraic  varieties which are distinguished  with respect to the polydisc. \end{enumerate} At the root of our work is the Berger--Coburn--Lebow theorem characterizing a commuting tuple of isometries. This work is in [1].  2. We have studied the action of the automorphism group of the $2$ complex dimensional manifold symmetrized bidisc $\mathbb G$ on itself. The automorphism group is $3$ real dimensional. It foliates $\mathbb G$ into leaves all of which are $3$ real dimensional hypersurfaces except one, viz., the royal variety. This leads us to investigate Isaev's classification of all Kobayashi-hyperbolic $2$ complex dimensional  manifolds for which the group of holomorphic automorphisms has real dimension $3$ studied by Isaev. Indeed, we produce a biholomorphism between the symmetrized bidisc and the domain  \[\{(z_1,z_2)\in \mathbb{C} ^2 : 1+|z_1|^2-|z_2|^2>|1+ z_1 ^2 -z_2 ^2|, Im(z_1 (1+\overline{z_2}))>0\}\]  in Isaev's list. Isaev calls it $\mathcal D_1$. The road to the biholomorphism is paved with various geometric insights about $\mathbb G$.    Several consequences of the biholomorphism follow including two new characterizations of the symmetrized bidisc and several new characterizations of $\mathcal D_1$. Among the results on $\mathcal D_1$, of particular interest is the fact that $\mathcal D_1$ is a ``symmetrization''. When we symmetrize (appropriately defined in this context) either $\Omega_1$ or $\mathcal{D}^{(2)} _1$ (Isaev's notation), we get $\mathcal D_1$.  These two domains $\Omega_1$ and $\mathcal{D}^{(2)} _1$ are in Isaev's list and he mentioned that these are biholomorphic to $\mathbb D \times \mathbb D$. We produce explicit biholomorphisms between these domains and $\mathbb D \times \mathbb D$. This work is in [2].  [1]  Distinguished Varieties Through the Berger--Coburn--Lebow Theorem,  co-authored with P. Kumar and H. Sau. Submitted to journal and arXiv link is https://arxiv.org/pdf/2001.01410.pdf   [2] An unbounded realization of the symmetrized bidisc, co-authored with A. Biswas and A. Maitra. Submitted to journal and arXiv link is  https://arxiv.org/pdf/2005.00289.pdf


\subsection{Vamsi Pritham Pingali}

My research during this period involved proving existence results for geometric PDE conditioned on some necessary and sufficient conditions. In [1], the dHYM equation on three-folds was studied, and in [2] we proved an existence result for the gravitating vortex equation conditioned on a GIT stability condition. In addition, some earlier works [3],[4],[5],[6] were accepted/published during this period.  [1] Pingali, Vamsi Pritham. "The deformed Hermitian Yang-Mills equation on three-folds." arXiv preprint arXiv:1910.01870 (2019). [2] Garcia-Fernandez, Mario, Vamsi Pritham Pingali, and Chengjian Yao. "Gravitating vortices with positive curvature." arXiv preprint arXiv:1911.09616 (2019). [3] PINGALI, V., & VAROLIN, D. (2019). NONUNIFORMLY FLAT AFFINE ALGEBRAIC HYPERSURFACES. Nagoya Mathematical Journal, 1-43. doi:10.1017/nmj.2019.2 (Published online on 2 April  2019) [4] Pingali, Vamsi Pritham. "A vector bundle version of the Monge-Ampère equation." Advances in Mathematics 360 (2020): 106921. (Published online on 22 January 2020) [5] Álvarez-Cónsul, Luis, Mario Garcia-Fernandez, Oscar García-Prada, and Vamsi Pritham Pingali. "Gravitating vortices and the Einstein–Bogomol’nyi equations." Mathematische Annalen (2020): 1-34. (Published online on 20 February 2020) [6] Pingali, Vamsi Pritham. "Quillen metrics and perturbed equations." Letters in Mathematical Physics (2020): 1-15. (Published online on 5 March 2020)


\subsection{Ved Datar}

In collaboration with Vamsi Pingali [1],  a numerical criteria for the existence of solutions to generalised Monge-Ampere equations is obtained  on projective manifolds. The class of equations studied encompasses certain well known equations such as the $J$-equation and the inverse Hessian equations. In particular, this extends and strengthens the deep result of Gao Chen on the $J$-equation, and also resolves a well-known conjecture of Gabor Szekelyhidi.   In a collaboration with Xin Fu and Jian Song [2], Kahler-Einstein metrics were constructed in the neighbourhoods of isolated log-canonical singularities, and the asymptotics to certain local models were studied. This builds on a program initiated by Kobayashi and others.    In a joint project with Harish Seshadri, a conjecture on the almost rigidity of the complex projective space has been formulated, and is being studied. If solved, this would be a Kahler analog of a famous theorem of Tobias Colding on the almost rigidity of the sphere. While some preliminary results have been obtained, this is still work in progress.  [1] (with Vamsi Pingali) A numerical criterion for generalised Monge-Ampere equations on projective manifolds, arXiv:2006.01530 [2] (with Xin Fu and Jian Song) On the Kahler-Einstein metric near isolated log-canonical singularity,  in  preparation\subsection{Ramesh Manna}




\subsection{Safdar Quddus}

Working on Equivariant Gauss Manin connection(joint with Chakraborty and Tang), one preprint.


\subsection{Bikramaditya Sahu}

A characterization of the family of secant lines to a hyperbolic quadric in PG(3,q), q odd [1]  [1] P. Pradhan and Bikramaditya Sahu, A characterization of the family of secant lines to a hyperbolic quadric in PG(3,q),q odd, Discrete Mathematics 343, (2020), 112044.   (LINC) https://www.sciencedirect.com/science/article/pii/S0012365X20302302?dgcid=author


\subsection{Arun Maiti}

Tiling of hyperbolic surfaces


\subsection{Anirudha Poria}

Given a positive weight function and an isometry map on a Hilbert spaces $\mathcal{H}$, we studied a class of linear maps which is a $g$-frame, $g$-Riesz basis and a $g$-orthonormal basis for  $\mathcal{H}$ with respect to $\mathbb{C}$ in terms of the weight function. We applied these results to study the frame for shift-invariant subspaces on the Heisenberg group in [1].  We established a few uncertainty principles for the Fourier and the short-time Fourier transforms. Also, we discussed an analogue of Donoho--Stark uncertainty principle and provided some estimates for the size of the essential support of the short-time Fourier transform in  [2].  We established the Cowling-Price's, Hardy's and Morgan's uncertainty principles for the Opdam-Cherednik transform on modulation spaces associated with this transform in [3].  [1] A. Poria, Positive weight function and classification of g-frames, Numer. Funct. Anal. Optim. 41(8): 950--968 (2020).  [2] A. Poria, Uncertainty Principles for the Fourier and the Short-Time Fourier Transforms, preprint arXiv:2004.04184 (2020).  [3] A. Poria, Uncertainty principles for the Opdam-Cherednik transform on modulation spaces, preprint arXiv:2005.14274 (2020).


\subsection{Gopal Datt}

The concept of meromorphic normality was studied with the aim of improving known results and establishing new sufficient conditions for a family of meromorphic mappings on a domain in $\mathbb{C}^m$ into some complex projective space to be meromorphically normal. Meromorphic normality is a notion of sequential compactness, introduced by Fujimoto, for the space of meromorphic mappings of a domain in $\mathbb{C}^m$ into a complex projective space. One of the central results of our paper [1], currently under peer-review, is as follows:  \begin{theorem}  Let $D$ be a domain in $\mathbb{C}^m$. Let $\mathcal{F}$ be a family of meromorphic mappings from $D$ into $\mathbb{P}^n$, $\mathcal{G}$ a family of holomorphic mappings from $D$ into $\mathbb{P}^n$, and $\mathcal{H}$ a collection of hyperplanes in $\mathbb{P}^n$. Suppose that, for each $f\in\mathcal{F}$, there exist a $g_f\in\mathcal{G}$ and a subset  $\{H_{1,\,f},\ldots,\,H_{2n+1,\,f}\}\subset \mathcal{H}$ such that   \begin{enumerate}    \item[$(a)$]  $f(D)\not\subset H_{k,\,f}$ for $k=\,1,\ldots,\,2n+1$;       \item[$(b)$] $\inf\{D(H_{1,\,f},\dots, H_{2n+1,\,f}): f\in\mathcal{F}\}>0$; and       \item[$(c)$] $\mathsf{supp}\,\nu(f, H_{k,\,f})\subseteq g_f^{-1}(H_{k,\,f})$        for $k=\,1,\ldots,\,2n+1$.       \end{enumerate} Furthermore, assume that for any mapping in the closure of $\mathcal{G}$, its range is not a subset of any hyperplane in the closure of $\mathcal{H}$. If $\mathcal{G}$ is normal, then $\mathcal{F}$ is meromorphically normal. \end{theorem}  The objects $\mathsf{supp}\,\nu(f, H_{k,\,f})$ refer to the support of certain non-negative divisors; these can be thought of as the sets $f^{-1}(H_{k,\,f}); g^{-1}(H_{k,\,f})" respectively.  1. G. Datt, Meromorphically normal families in several variables, submitted for publication.  (A version of this article is available in arXiv with the title "Meromorphically normal families and a meromorphic Montel--Carath{\'e}odory theorem", arXiv:1812.0581)


\subsection{Sudip Bera}

Combinatorics


\subsection{Kiran Kumar Behera}

I worked on linear combinations of certain class of orthogonal polynomials called polynomials of $R_I$ type. Conditions were derived under which these linear combinations are again of $R_I$ type. In case they are not, they are shown to be related to another class of polynomials which are orthogonal with respect to a measure supported on the unit circle and having zeros of modulus one [1].  Thereafter, I began work on linear pencil matrix with Dr. Maxim Derevyagin  (University of Connecticut, USA) with a goal to obtain finite and infinite generalizations of a scalar parameter used in the theory of orthogonal polynomials. This manuscript is in progress.  [1]. K. K. B., Self-inversive polynomials from rational transformation of linear         functionals. Communicated. Available at arxiv.org/abs/1909.12548


\subsection{Sumana Hatui}

In [1], we explicitly computed Schur multiplier of special p-groups of rank 2. In [2], we study the Schur multiplier of the discrete as well as the finite Heisenberg groups and their t-variants. We describe the representation groups of these Heisenberg groups and through these give a construction of their finite dimensional complex projective irreducible representations.   [1] Sumana Hatui, Schur multipliers of special p-groups of rank 2, Journal of Group Theory, 23 (2020), 85-95. doi: 10.1515/jgth-2019-0045 [2] Sumana Hatui, Pooja Singla, On Schur multiplier and Projective representations of Heisenberg groups, (Submitted) arXiv:1909.06589 .


\subsection{Anwoy Maitra}

I worked on the problem of the continuous extension of isometries with respect to the Kobayashi distance in several complex variables. In particular, in the paper [1], I proved a generalization of an existing result [2, Theorem 2.18] of A. Zimmer. [1] Anwoy Maitra, On the continuous extension of Kobayashi isometries, Proc. Amer. Math. Soc. 148 (2020), 3437--3451. [2] Andrew M. Zimmer, Characterizing domains by the limit set of their automorphism group, Adv. Math. 308 (2017), 438--482.


\subsection{Samrat Sen}

I have worked on generalizing a kernel decomposition theorem of Hilbert modules in $\mathcal{B}_1(\Omega)$. With this generalization, I have produced geometric(unitary) invariants of a certain class of submodules of analytic Hilbert modules. I have also shown that an alternating sum of currents is a similarity invariant of these classes of submodules.


\subsection{Dr. Srijan Sarkar}

\begin{document}  Let $T = (T_1, \ldots, T_n)$ be a commuting tuple of bounded linear operators on a Hilbert space $\mathcal{H}$. The multiplicity of $T$ is the cardinality of a minimal generating set with respect to $T$ and is denoted by $\mbox{mult}_{T}(\mathcal{H})$. In the paper \cite{CSS}, we have established an additive formula for multiplicities of a class of commuting tuples of operators. A special case of the main result states the following: Let $n \geq 2$, and let $\mathcal{Q}_i$, $i = 1, \ldots, n$, be a proper closed shift co-invariant subspaces of the Dirichlet space or the Hardy space over the unit disc in $\mathbb{C}$. If $\mathcal{Q}_i^{\perp}$, $i = 1, \ldots, n$, is a zero-based shift invariant subspace, then the multiplicity of the joint $M_{\bm z} = (M_{z_1}, \ldots, M_{z_n})$-invariant subspace $(\mathcal{Q}_1 \otimes \cdots \otimes \mathcal{Q}_n)^{\perp}$ of the Dirichlet space or the Hardy space over the unit polydisc in $\mathbb{C}^n$ is given by \[ \mbox{mult}_{M_{\bm z}|_{ (\mathcal{Q}_1 \otimes \cdots \otimes \mathcal{Q}_n)^\perp}} \big((\mathcal{Q}_1 \otimes \cdots \otimes \mathcal{Q}_n)^\perp \big) = \sum_{i=1}^n (\mbox{mult}_{M_z|_{\mathcal{Q}_i^{\perp}}} (\mathcal{Q}_i^{\perp})) = n. \] A similar result holds for the Bergman space over the unit polydisc.  \begin{thebibliography}{99}  \bibitem{CSS} Chattopadhyay A., Sarkar J. and Sarkar S., {\em Multiplicities, invariant subspaces and an additive formula}, https://arxiv.org/abs/1812.05435.  \end{thebibliography}   \end{document}


\subsection{Projesh Nath Choudhury}

(1)  N-matrices are real $n\times n$ matrices all of whose principal  minors are negative. We provide (i) an $O(2^n)$ test to detect whether or not a given matrix is an N-matrix, and (ii) a characterization of N-matrices, leading to the recursive construction of every N-matrix.  (2) Matrices with the property that the real part is positive definite, have been studied for the past five decades or more. Many results in the form of inequalities have been obtained for matrices possessing this property. In this joint work, a new class of matrices, viz., matrices whose real part is positive semidefinite, is considered, wherein extensions of the results in the literature are obtained.


\subsection{Sneh Bala Sinha}

[1] Chim, Kwok Chi; Shorey, Tarlok Nath; Sinha, Sneh Bala ,On Baker's Explicit $abc$-conjecture,  Publ. Math. Debrecen 94 (2019), no. 3-4, 435–453.  We derived from Baker's explicit $abc$-conjecture that $a+b=c$ where $a$, $b$ and $c$ are relatively prime positive integers %\eqref{eq_OM}  implies that $c < N^{1.72}$ for $N \geq 1$ and $c < 32 N^{1.6}$ for $N \geq 1$. This sharpens an estimate of Laishram and Shorey. We also show that it implies $c < \frac{6}{5}N^{1+G(N)} $ for $N \geq 3$ and $c < \frac{6}{5}N^{1+G_1(N)}$ for $N \geq 297856$ where $G(N)$ and $G_1(N)$ are explicitly given positive valued decreasing functions of $N$ tending to zero as $N$ tends to infinity.  Finally we give applications of our estimates on  triples of consecutive powerful integers and generalized Fermat equation.


\subsection{Gouranga Mallik}

The Morley finite element method (FEM) is attractive for semilinear problems with the biharmonic operator as a leading term in the stream function vorticity formulation of two-dimensional Navier–Stokes problem and in the von Kármán equations. This paper establishes a best-approximation a priori error analysis and an a posteriori error analysis of discrete solutions close to an arbitrary regular solution on the continuous level to semilinear problems with a trilinear nonlinearity. The analysis avoids any smallness assumptions on the data, and so has to provide discrete stability by a perturbation analysis before the Newton–Kantorovich theorem can provide the existence of discrete solutions. An abstract framework for the stability analysis in terms of discrete operators from the medius analysis leads to new results on the nonconforming Crouzeix–Raviart FEM for second-order linear nonselfadjoint and indefinite elliptic problems. The paper identifies six parameters and sufficient conditions for the local a priori and a posteriori error control of conforming and nonconforming discretizations of a class of semilinear elliptic problems first in an abstract framework and then in the two semilinear applications. This leads to new best-approximation error estimates and to a posteriori error estimates in terms of explicit residual-based error control for the conforming and Morley FEM. For more details see [1].  Lower-order quadratic finite elements are popular for solving fourth-order elliptic PDEs when the solution has limited regularity.  A priori and a posteriori error estimates are considered in Carstensen et al. [1] with respect to different mesh dependent norms which involve different jump and penalization terms. This work addresses the question, whether they are comparable with respect to a common norm. This article  establishes that the errors for the quadratic symmetric interior discontinuous Galerkin, C0 interior penalty and nonconforming Morley finite element methods are equivalent upto some higher-order oscillation term with respect to a unified norm. Numerical experiments are performed to substantiate the comparison results. Paper under preparation.  A unified framework for goal-oriented a posteriori error estimation is derived for the biharmonic problem. In particular, C0IP and discontinuous Galerkin finite element methods are considered. The quantity of interest is given by a functional composed of a volumetric weighted mean value. The estimator is based on potential reconstruction and equilibrated moment tensor that gives a  guaranteed upper bound of error. Paper under preparation.  1. Carsten Carstensen, Gouranga Mallik and Neela Nataraj, Nonconforming Finite Element Discretization for Semilinear Problems with Trilinear Nonlinearity, IMA Journal of Numerical Analysis, 2020.


\subsection{Surjit Kumar}

In a continuation of the project "Operator valued multishifts" together with Rajeev Gupta and Shailesh Trivedi , we establish circularity, analyticity and wandering subspace property of these multishifts. Further, we study the function theoretic behaviour of operator-valued multishifts. We determine the bounded point evaluation, reproducing kernel structure and the unitary equivalence of operator-valued multishifts with invertible operator weights (see [2]).   In a joint work with Soumitra Ghara and Paramita Pramanick, we have generalized the notion of so called Spherical tuple of operators, namely $K$-homogeneous operator tuple, where $K$ is the maximal compact subgroup of the identity component of the biholomorphic automorphism group of irreducible bounded symmetric domain. In this work [2], we obtain a model for a certain class of $K$-homogeneous operator tuple as the operators of multiplication by the coordinate on a reproducing kernel Hilbert space of holomorphic functions. Using this model, we obtain a criterion for boundedness, membership in the Cowen-Douglas class, unitary equivalence and similarity of these tuples.  [1] Rajeev Gupta, Surjit Kumar and Shailesh Trivedi “Unitary equivalence of Operator-Valued Multishifts “, J. Math. Anal. Appl. (2020). [2] Soumitra Ghara, Surjit Kumar and Paramita Pramanick “$K$-homogeneous tuple of operators on bounded symmetric domains, preprint.


\subsection{Debmalya Sain}

Possible applications of the approximate version of the Birkhoff-James orthogonality have been explored in [1]. In [2], we have conducted a study of the geometric properties, including parallelism and orthogonality, in operator spaces. Various analytic applications of the concept of orthogonality have been presented in the Book Chapter [3]. Symmetry of Birkhoff-James orthogonality in operator spaces has been discussed in the Book Chapter [4]. Extreme contractions and their connection with the operator norm attainment set is the subject matter of [5]. The article [6] deals with Bishop-Phelps-Bolloboas type theorems in operator spaces. The numerical index of polyhedral banach spaces is the main object of study in [7]. The article [8] is concerned with approximate Birkhoff-James orthogonality and normal cones in a normed space. Norm optimization problems in operator spaces have been investigated in [9]. We have studied geometric properties of extreme contractions between polygonal Banach spaces in [10]. A complete characterization of the operator norm attainment set has been obtained in [11]. Bhatia-Semrl type theorems have been studied in the general setting of Banach spaces in [12].    [1] Mal, Arpita and Paul, Kallol and Rao, T. S. S. R. K. and Sain, Debmalya, Approximate Birkhoff-James orthogonality and smoothness in the space of bounded linear operators, Monatsh. Math. , 190 (2019), 549-558.  [2] Mal, Arpita and Sain, Debmalya and Paul, Kallol, On some geometric properties of operator spaces, Banach J. Math. Anal. , 13 (2019), 174-191.   [3] Paul, Kallol and Sain, Debmalya, Birkhoff-James orthogonality and its application in the study of geometry of Banach space, Advanced topics in mathematical analysis , (2019), 245-284.  [4] Paul, Kallol and Sain, Debmalya and Ghosh, Puja, Symmetry of Birkhoff-James orthogonality of bounded linear operators, Ulam type stability , (2019), 331-344.  [5] Sain, Debmalya, On extreme contractions and the norm attainment set of a bounded linear operator, Ann. Funct. Anal. , 10 (2019), 135-143.  [6] Sain, Debmalya, Smooth points in operator spaces and some Bishop-Phelps-Bollobás type theorems in Banach spaces, Oper. Matrices , 13 (2019), 433-445.  [7] Sain, Debmalya and Paul, Kallol and Bhunia, Pintu and Bag, Santanu, On the numerical index of polyhedral Banach spaces, Linear Algebra Appl. , 577 (2019), 121-133.  [8] Sain, Debmalya and Paul, Kallol and Mal, Arpita, On approximate Birkhoff-James orthogonality and normal cones in a normed space, J. Convex Anal. , 26 (2019), 341-351.  [9] Sain, Debmalya and Paul, Kallol and Mandal, Kalidas, On two extremum problems related to the norm of a bounded linear operator, Oper. Matrices , 13 (2019), 421-432.  [10] Sain, Debmalya and Ray, Anubhab and Paul, Kallol, Extreme contractions on finite-dimensional polygonal Banach spaces, J. Convex Anal. , 26 (2019), 877-885.  [11] Sain, Debmalya, On the norm attainment set of a bounded linear operator and semi-inner-products in normed spaces, Indian J. Pure Appl. Math. , 51 (2020), 179-186.  [12] Sain, Debmalya and Mal, Arpita and Paul, Kallol, Some remarks on Birkhoff-James orthogonality of linear operators, Expo. Math. , 38 (2020), 138-147.


\subsection{Dr. Abhitosh Upadhyay}




\subsection{Anupam Gumber}

I have been working as a NBHM-postdoctoral fellow at IISc Bangalore under the mentorship of  Prof. S. Thangavelu since March 28, 2019. During the period between April 01, 2019-March 31, 2020 at IISc, along with some research discussions with Prof. S. Thangavelu, I was also involved in working on research problems jointly with Prof. P. K. Ratnakumar (HRI Prayagraj, India), Prof. Joachim Toft (Linnaeus Univ., Sweden) and Prof. Hans G. Feichtinger (NuHAG Group Leader, Univ. Vienna, Austria). The questions considered require the interplay between harmonic analysis, time-frequency analysis and approximation theory. The following is a brief detailed report of my research work during the above mentioned period at IISc:   \begin{itemize} \item [(I)] {\large{\bf Translation and modulation invariant Hilbert spaces:}} In a joint work with Prof. Joachim Toft and other collaborators, we have investigated the translation and modulation invariant Hilbert spaces. In this regard, we have shown that any Hilbert space of distributions on $\mathbb{R}^d$ which is translation and modulation invariant, also in the sense of its norm, is equal to $L^2(\mathbb{R}^d)$, with the same norm apart from a multiplicative constant. The manuscript has been communicated to a journal.   \item [(II)] {\large{\bf On Weyl multipliers and twisted modulation spaces:}} In a joint collaboration with Prof. P. K. Ratnakumar, we have studied the twisted modulation spaces and characterise the Weyl multipliers on them. The analysis also leads to the characterisation of multiplication operators on certain non-commutative amalgam spaces. The technical work relies on the harmonic analysis of special Hermite operator, also called the twisted Laplacian on $\mathbb{C}^n$. The manuscript is to be submitted soon.  \item [(III)] {\large{\bf{Completeness of shifted dilates in invariant Banach spaces of distributions:}}} Jointly with Prof. Hans G. Feichtinger,  we  show that the well established methods from the theory of Banach modules and time-frequency analysis allow to derive completeness results for the collection of shifted and dilated version of a given (test) function in a quite general setting. While the basic ideas show strong similarity to the arguments used in a recent paper by V. Katsnelson [1], we extend his results in several directions, both relaxing the assumptions (instead of a Gauss function any function with non-vanishing integral can be used), and widening the range of applications considerably. There is no need for the Banach spaces considered to be embedded into $(L^2(\mathbb{R}), ||\cdot{}||_2 )$, nor is the Hilbert space structure relevant. We choose to present the results in the setting of the Euclidean spaces, because then the  space of tempered distributions $S^{\prime}(\mathbb{R}^d) (d \geq 1)$  provides a well-established environment for mathematical analysis. In addition, we establish connections to modulation spaces, and specifically to the Shubin classes $(Q_s(\mathbb{R}^d), ||\cdot{}||_{Q_s})$, by showing that they are indeed special cases of Katsnelson's setting. The technical work for the results involved is almost done. The final writing of the manuscript is in progress. \end{itemize}  References: [1] V. Katsnelson, On the completeness of Gaussians in a Hilbert functional space, {\em Complex Anal. Oper. Theory}, 13(3) (2019) 637-658.